\hypertarget{namespace_rocketry}{}\section{Rocketry Namespace Reference}
\label{namespace_rocketry}\index{Rocketry@{Rocketry}}


\subsection{Detailed Description}
The template for displaying 404 pages (not found).

The template for displaying archive pages.

Learn more\+: \href{http://codex.wordpress.org/Template_Hierarchy}{\tt http\+://codex.\+wordpress.\+org/\+Template\+\_\+\+Hierarchy}

The template for displaying comments.

The area of the page that contains both current comments and the comment form.

The template part for displaying a message that posts cannot be found.

Learn more\+: \href{http://codex.wordpress.org/Template_Hierarchy}{\tt http\+://codex.\+wordpress.\+org/\+Template\+\_\+\+Hierarchy}

The template used for displaying page content in page.\+php

The template part for displaying results in search pages.

Learn more\+: \href{http://codex.wordpress.org/Template_Hierarchy}{\tt http\+://codex.\+wordpress.\+org/\+Template\+\_\+\+Hierarchy}

The template for displaying the footer.

Contains the closing of the \#content div and all content after

\hyperlink{namespace_rocketry}{Rocketry} functions and definitions

The header for our theme.

Displays all of the $<$head$>$ section and everything up till 

Sample implementation of the Custom Header feature \href{http://codex.wordpress.org/Custom_Headers}{\tt http\+://codex.\+wordpress.\+org/\+Custom\+\_\+\+Headers}

You can add an optional custom header image to header.\+php like so ...

 $<$?php if ( get\+\_\+header\+\_\+image() ) \+: ?$>$ \href{<?php echo esc_url( home_url( '/' ) ); ?>}{\tt } $<$?php endif; // End header image check. ?$>$

\hyperlink{namespace_rocketry}{Rocketry} Theme Customizer

Custom functions that act independently of the theme templates

Eventually, some of the functionality here could be replaced by core features

Jetpack Compatibility File See\+: \href{http://jetpack.me/}{\tt http\+://jetpack.\+me/}

Custom template tags for this theme.

Eventually, some of the functionality here could be replaced by core features.

The main template file.

This is the most generic template file in a Word\+Press theme and one of the two required files for a theme (the other being style.\+css). It is used to display a page when nothing more specific matches a query. E.\+g., it puts together the home page when no home.\+php file exists. Learn more\+: \href{http://codex.wordpress.org/Template_Hierarchy}{\tt http\+://codex.\+wordpress.\+org/\+Template\+\_\+\+Hierarchy}

The template for displaying all pages.

This is the template that displays all pages by default. Please note that this is the Word\+Press construct of pages and that other \textquotesingle{}pages\textquotesingle{} on your Word\+Press site will use a different template.

The template for displaying search results pages.

The sidebar containing the main widget area.

The template for displaying all single posts. 